Measurement Bias from Address Aliasing

### 2016-01-07 paper.tex
Tuned the spacing of figures/tables.
Fixed overlap in BLAS item list.

% paper.tex
% ACM sigmetric format
% Author: L. K. Melhus and R. E. Jensen
%\documentclass{acm_proc_article-sp}
\documentclass[10pt, conference, compsocconf]{IEEEtran}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
\usepackage{tikz}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{underscore}
\usepackage{url}
\usepackage{lmodern} % Much clearer text
\usepackage[utf8]{inputenc}
\usepackage{hyperref} % For PDF metadata
%\usepackage{enumitem} % Controlling list styling
\usepackage[font=small,skip=0pt]{caption}
%http://tex.stackexchange.com/questions/94016/how-to-reduce-space-between-image-and-its-caption

@@

%\newpage
\section{Aliasing in Real Applications}
\label{sec:blas}
To investigate how real world applications can be impacted by aliasing, we look at low level numerical applications.
Basic Linear Algebra Subroutines (BLAS) is the de facto standard API for high performance linear algebra routines, with several heavily optimized implementations available~\cite{Blackford:2002:UpdatedBLAS}.
The functionality is divided into three categories:
\begin{description}
  \item[Level 1] Scalar and vector operations, such as dot product and vector addition.
  \item[Level 2] Matrix-vector operations, such as gemv for general matrix-vector multiplication.
  \item[Level 3] Matrix-matrix operations, including the widely applied gemm routine for general matrix multiplication.
\end{description}
Procedures operating on vectors, from level 1 or 2, intuitively appears the most likely to have potential for aliasing.

>>>>

% paper.tex
% ACM sigmetric format
% Author: L. K. Melhus and R. E. Jensen
%\documentclass{acm_proc_article-sp}
\documentclass[10pt, conference, compsocconf]{IEEEtran}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
\usepackage{tikz}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{underscore}
\usepackage{url}
\usepackage{lmodern} % Much clearer text
\usepackage[utf8]{inputenc}
\usepackage{hyperref} % For PDF metadata
%\usepackage{enumitem} % Controlling list styling
%\usepackage[font=small,skip=0pt]{caption}
%http://tex.stackexchange.com/questions/94016/how-to-reduce-space-between-image-and-its-caption
\usepackage[font=small,belowskip=-10pt,aboveskip=0pt]{caption}

%\setlength{\intextsep}{10pt plus 2pt minus 2pt}

%\setlength{\belowcaptionskip}{-5pt}
% too much?

%\captionsetup[table]{aboveskip=-25pt}

%\setlength{\dblfloatsep}{-15pt}

%\addtolength{\belowcaptionskip}{15pt}

@@

%\newpage
\section{Aliasing in Real Applications}
\label{sec:blas}
To investigate how real world applications can be impacted by aliasing, we look at low level numerical applications.
Basic Linear Algebra Subroutines (BLAS) is the de facto standard API for high performance linear algebra routines, with several heavily optimized implementations available~\cite{Blackford:2002:UpdatedBLAS}.
The functionality is divided into three categories:
\begin{description}
  \item[Level 1] \hspace{0.1cm} Scalar and vector operations, such as dot product and vector addition.
  \item[Level 2] \hspace{0.1cm} Matrix-vector operations, such as gemv for general matrix-vector multiplication.
  \item[Level 3] \hspace{0.1cm} Matrix-matrix operations, including the widely applied gemm routine for general matrix multiplication.
\end{description}
Procedures operating on vectors, from level 1 or 2, intuitively appears the most likely to have potential for aliasing.
